Thesis Title

### 2022-03-18 chapters/introduction.tex
add paper 1

As explored in \secref{ssec:reads_2_genomes}, longer sequences are more informative than shorter sequencing data, as the one obtained from second-generation sequencing (see \secref{ssec:2nd_gen_seq}), and can provide a more complete picture of the microbial community in a given samples. 
Several dedicated metagenomic assembly tools are available, such as metaSPAdes\footnote{\url{}}  and MegaHIT\footnote{\url{}} \citep{nurk_metaspades_2017, li_megahit_2015}. 
These tools, in comparison to single-cell data assemblers, are better at dealing with the combination of intragenomic and intergenomic repeats and uneven sequencing coverage \citep{olson_metagenomic_2017}.

\subsubsection{Trash text}

>>>>

As explored in \secref{ssec:reads_2_genomes}, longer sequences are more informative than shorter sequencing data, as the one obtained from second-generation sequencing (see \secref{ssec:2nd_gen_seq}), and can provide a more complete picture of the microbial community in a given samples. 
Several dedicated metagenomic assembly tools are available, such as metaSPAdes\footnote{\url{}}  and MegaHIT\footnote{\url{}} \citep{nurk_metaspades_2017, li_megahit_2015}. 
These tools, in comparison to single-cell data assemblers, are better at dealing with the combination of intra and intergenomic repeats and uneven sequencing coverage \citep{olson_metagenomic_2017}.

\section{Trash text}

### 2022-03-18 main.tex
add to genomics in introduction
Updates from Overleaf
update
updates do introduction  - metagenomics
minor fixes
add paper 1

%-----------------------------------------------------------------
% Preamble
%------------------------------------------------------------------
\documentclass[12pt,a4paper,twoside,openright]{book}
\usepackage{mathptmx} % times no roman-like font
\usepackage[left=30mm, right=25mm, top=25mm, bottom=25mm]{geometry} % margins
\pagestyle{fancy}
\renewcommand{\baselinestretch}{1.15}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\graphicspath{{figures/}}
\def\blankpage{%
      \clearpage%
      \thispagestyle{empty}%
      \null%
      \clearpage}

%-----------------------------------------------------------------
% Packages
%------------------------------------------------------------------
\usepackage{setspace}
\usepackage{fancyhdr}
\renewcommand{\chaptermark}[1]{\markboth{\MakeUppercase{\thechapter. #1 }}{}}
\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}}
\usepackage{titlesec}
\fancyhf{}
\fancyhead[RO]{\bfseries\rightmark}
\fancyhead[LE]{\bfseries\leftmark}
\setlength{\headheight}{15pt}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\headheight}{0.5pt}
\fancypagestyle{plain}{
  \fancyhead{}
  \renewcommand{\headrulewidth}{0pt}
}
\usepackage{hyperref} % To add urls
\usepackage{graphicx} % To add images
\usepackage[nottoc]{tocbibind}
\usepackage[backend=biber,style=authoryear,maxcitenames=1,autocite=inline,natbib=true,sorting=nty]{biblatex} % References
\addbibresource{references.bib}
\usepackage{indentfirst} % Add indentation to first paragraph
\setlength{\parskip}{1em}
\setcounter{tocdepth}{3}
\setcounter{secnumdepth}{3}
\usepackage{enumitem}
\usepackage[font=footnotesize]{caption}
\usepackage[toc,page]{appendix}
\usepackage{pdfpages}
\usepackage{fmtcount}
\usepackage{url}
\usepackage{amsmath}
\usepackage{bm}
\usepackage[utf8]{inputenc}
\usepackage{filecontents}
\usepackage{float}
\raggedbottom
\usepackage{subcaption}
\usepackage{eurosym}
\usepackage{booktabs}
\usepackage[T1]{fontenc}
\usepackage[acronym]

\makeatletter
\def\cleardoublepage{\clearpage\if@twoside \ifodd\c@page\else
    \hbox{}
    \thispagestyle{plain}
    \newpage
    \if@twocolumn\hbox{}\newpage\fi\fi\fi}
\makeatother \clearpage{\pagestyle{plain}\cleardoublepage}

\providecommand{\keywords}[1]{\textbf{Keywords:} #1}
\providecommand{\keywordsP}[1]{\textbf{Palavras chave:} #1}

@@

%-----------------------------------------------------------------
% Dedication
%------------------------------------------------------------------
\newpage
\thispagestyle{empty}
\vspace*{3cm}
\begin{center}
\emph{``I'm so happy to be done with this shit''} \\
\end{center} 
\begin{flushright}- Inês Mendes\end{flushright}
\clearpage \thispagestyle{empty}\mbox{}\clearpage

@@

%-----------------------------------------------------------------
% Table of Contents
%------------------------------------------------------------------
\newpage
\thispagestyle{plain}
\addcontentsline{toc}{chapter}{Table of Contents}
\renewcommand{\contentsname}{Table of Contents}
\tableofcontents
\clearpage \thispagestyle{empty}\mbox{}\clearpage
\newpage
\thispagestyle{plain}
\listoftables
\clearpage \thispagestyle{empty}\mbox{}\clearpage
\newpage
\thispagestyle{plain}
\listoffigures
\clearpage \thispagestyle{empty}\mbox{}\clearpage

@@

%-----------------------------------------------------------------
% Introduction
%------------------------------------------------------------------
\newpage
\thispagestyle{empty}
\chapter{General Introduction\label{ch:introduction}}
\thispagestyle{empty}
\newpage
\begin{refsection}
\include{chapters/introduction}
\newpage
\printbibliography
\end{refsection}

@@

%-----------------------------------------------------------------
% Appendix
%-----------------------------------------------------------------
\appendix
\chapter{Appendix}
\include{chapters/appendix}
\includepdf[pages={1-}]{resources/papers/s41598-018-31873-w.pdf}
\includepdf[pages={1-}]{resources/papers/dkz363.pdf}
\includepdf[pages={1-}]{resources/papers/mgen000328.pdf}

>>>>

%-----------------------------------------------------------------
% Preamble
%------------------------------------------------------------------
\documentclass[12pt,a4paper,twoside,openright]{book}
\usepackage{mathptmx} % times no roman-like font
\usepackage[left=30mm, right=25mm, top=25mm, bottom=25mm]{geometry} % margins
\usepackage{setspace}
\usepackage{fancyhdr}
\pagestyle{fancy}
\renewcommand{\baselinestretch}{1.15}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\graphicspath{{figures/}}
\def\blankpage{%
      \clearpage%
      \thispagestyle{empty}%
      \null%
      \clearpage}

%-----------------------------------------------------------------
% Packages
%------------------------------------------------------------------
\renewcommand{\chaptermark}[1]{\markboth{\MakeUppercase{\thechapter. #1 }}{}}
\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}}
\usepackage{titlesec}
\fancyhf{}
\fancyhead[RO]{\bfseries\rightmark}
\fancyhead[LE]{\bfseries\leftmark}
\setlength{\headheight}{15pt}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\headheight}{0.5pt}
\fancypagestyle{plain}{
  \fancyhead{}
  \renewcommand{\headrulewidth}{0pt}
}
\usepackage{hyperref} % To add urls
\usepackage{graphicx} % To add images
\usepackage[nottoc]{tocbibind}
\usepackage[backend=biber,style=authoryear,maxcitenames=1,autocite=inline,natbib=true,sorting=nty]{biblatex} % References
\addbibresource{references.bib}
\usepackage{indentfirst} % Add indentation to first paragraph
\setlength{\parskip}{1em}
\setcounter{tocdepth}{4}
\setcounter{secnumdepth}{4}
\usepackage{enumitem}
\usepackage[font=footnotesize]{caption}
\usepackage[toc,page]{appendix}
\usepackage{pdfpages}
\usepackage{fmtcount}
\usepackage{url}
\usepackage{amsmath}
\usepackage{bm}
\usepackage[utf8]{inputenc}
\usepackage{filecontents}
\usepackage{float}
\raggedbottom
\usepackage{subcaption}
\usepackage{eurosym}
\usepackage{booktabs}
\usepackage[T1]{fontenc}
\usepackage[acronym]
\makeatletter
\def\cleardoublepage{\clearpage\if@twoside \ifodd\c@page\else
    \hbox{}
    \thispagestyle{plain}
    \newpage
    \if@twocolumn\hbox{}\newpage\fi\fi\fi}
\makeatother \clearpage{\pagestyle{plain}\cleardoublepage}

\providecommand{\keywords}[1]{\textbf{Keywords:} #1}
\providecommand{\keywordsP}[1]{\textbf{Palavras chave:} #1}
\newcommand{\secref}[1]{\autoref{#1}. \nameref{#1}}
\usepackage{lscape}
\usepackage{adjustbox}
\usepackage{booktabs}
\usepackage{graphicx}

@@

%-----------------------------------------------------------------
% Dedication
%------------------------------------------------------------------
\newpage
\thispagestyle{empty}
\vspace*{3cm}
\begin{center}
\emph{"The greatest adventure is what lies ahead.\\
Today and tomorrow are yet to be said.\\
The chances, the changes are all yours to make.\\
The mould of your life is in your hands to break."} \\
\end{center} 
\begin{flushright}-J. R. R. Tolkien, The Hobbit\end{flushright}
\clearpage \thispagestyle{empty}\mbox{}\clearpage

@@

%-----------------------------------------------------------------
% Table of Contents
%------------------------------------------------------------------
\newpage
\thispagestyle{plain}
\addcontentsline{toc}{chapter}{Table of Contents}
\renewcommand{\contentsname}{Table of Contents}
\tableofcontents
\clearpage \thispagestyle{empty}\mbox{}\clearpage
\newpage
\thispagestyle{plain}
\listoftables
\clearpage \thispagestyle{empty}\mbox{}\clearpage
\newpage
\thispagestyle{plain}
\listoffigures
%\clearpage \thispagestyle{empty}\mbox{}\clearpage

@@

%-----------------------------------------------------------------
% Introduction
%------------------------------------------------------------------
\newpage
\thispagestyle{empty}
\chapter{General Introduction\label{ch:introduction}}
\thispagestyle{empty}
\clearpage \thispagestyle{empty}\mbox{}\clearpage
\newpage
\begin{refsection}
\include{chapters/introduction}
\newpage
\printbibliography
\end{refsection}

%-----------------------------------------------------------------
% Paper 1
%------------------------------------------------------------------
\newpage
\thispagestyle{empty}
\chapter{Critical steps in clinical shotgun metagenomics for the concomitant detection and typing of microbial pathogens\label{ch:paper1}}

\thispagestyle{empty}
\clearpage \thispagestyle{empty}\mbox{}\clearpage
\newpage
\begin{refsection}
\include{chapters/paper1}
\newpage
\printbibliography
\end{refsection}

@@

%-----------------------------------------------------------------
% Appendix
%-----------------------------------------------------------------
\appendix
\chapter{Appendix}
\include{chapters/appendix}
%\includepdf[pages={1-}]{resources/papers/s41598-018-31873-w.pdf}
%\includepdf[pages={1-}]{resources/papers/dkz363.pdf}
%\includepdf[pages={1-}]{resources/papers/mgen000328.pdf}
